Index measures for oak decline severity using phenotypic descriptors

### 2019-12-12 manuscript/manuscript.Rmd
Methods and results rearrange. Added site details

- Site types
- Field phenotyping protocol
- Crown assessments
- Stem assessments - 2m base, 3m base

Phenotypic data were collected from a total of 174 trees from 9 sites from across the south, east and west of England.

@@

### Machine learning analyses

### Phenotypic descriptors for oak decline

### Tree size descriptor adjustment by site

@@

Proximity matrix (*P*) was transformed to a dissimilarity (1 - *P*) then multidimensional scaling (MDS) to 2 dimensions applied.
The first dimension was found to be related to the overall severity of decline.
It was min-max scaled to give the PDI a scale between 0 and 1 with more severely declining trees having a score closer to 1.
The second MDS dimension was found to be associated with  min-max scaled to give scores between -1 and 1 with chronically declining trees having a score closer to -1 and acutely declining trees having a score closer to 1. 
Trees with a score around 0 are neither distinctively AOD or COD sharing characteristics of both conditions in trees with PDI greater than 0.3.
A significant difference was found in the PDI between non-symptomatic (control) and symptomatic (AOD and COD) decline statuses using an independant two sample t-test (`r glue("t({PDI_status_ttest$parameter}) = {signif(PDI_status_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(PDI_status_ttest$estimate1,digits = 3)` and `r signif(PDI_status_ttest$estimate2,digits = 3)` for non-symptomatic and symptomatic statuses respectively.
Significance was also found in the DAI between the AOD and COD groups (`r glue("t({DAI_groups_ttest$parameter}) = {signif(DAI_groups_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(DAI_groups_ttest$estimate1,digits = 3)` and `r signif(DAI_groups_ttest$estimate2,digits = 3)` for the AOD and COD groups respectively.
A scatter plot of PDI against DAI is shown in Figure # for all 174 trees.
It can clearly be seen that the

>>>>

- Site types
- Field phenotyping protocol
- Crown assessments
- Other assessments

Phenotypic data were collected from a total of 174 trees from nine sites from across the south, east and west of England between June and September in 2016 or 2017.
The occurance of AOD has previously been reported and studied at six of the sites [@brown2016; @brown2017].

@@

### Tree size descriptor adjustment for age and inter site variance

@@

Proximity matrix (*P*) was transformed to a dissimilarity (1 - *P*) then multidimensional scaling (MDS) to 2 dimensions applied.
The first dimension was found to be related to the overall severity of decline.
It was min-max scaled to give the PDI a scale between 0 and 1 with more severely declining trees having a score closer to 1.
The second MDS dimension was found to be associated with  min-max scaled to give scores between -1 and 1 with chronically declining trees having a score closer to -1 and acutely declining trees having a score closer to 1. 
Trees with a score around 0 are neither distinctively AOD or COD sharing characteristics of both conditions in trees with PDI greater than 0.3.

###

### Site differences

### Oak decline indexes

A significant difference was found in the PDI between non-symptomatic (control) and symptomatic (AOD and COD) decline statuses using an independant two sample t-test (`r glue("t({PDI_status_ttest$parameter}) = {signif(PDI_status_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(PDI_status_ttest$estimate1,digits = 3)` and `r signif(PDI_status_ttest$estimate2,digits = 3)` for non-symptomatic and symptomatic statuses respectively.
Significance was also found in the DAI between the AOD and COD groups (`r glue("t({DAI_groups_ttest$parameter}) = {signif(DAI_groups_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(DAI_groups_ttest$estimate1,digits = 3)` and `r signif(DAI_groups_ttest$estimate2,digits = 3)` for the AOD and COD groups respectively.
A scatter plot of PDI against DAI is shown in Figure # for all 174 trees.
It can clearly be seen that the
